\textbf{Computational Fuzzy Extractors}

### 2013-09-04 trunk/CompFuzzExt.tex
Removing dead text from tex file

Authentication generally requires a secret drawn from some high-entropy source.  One of the primary building blocks for authentication is reliable key derivation.  Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  %Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).  The setting 
%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).  The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.  This information allows
the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.  This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.  The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$. 
A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.

@@

The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.  Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.  
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

@@

%%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high. 
%The minimum entropy loss for secure sketches has been quantified in past work.  Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}, 
%%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
%the entropy loss of a secure sketch that can reconcile $t$ errors
% %with high probability 
% is bounded by the redundancy of
%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  Constructions of fuzzy extractors that use a secure sketch inherit this bound.
%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.  This string $\recout$ is  required to have high HILL entropy even conditioned on $s$. Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.

@@

%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application}

@@

\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.  They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.  One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.   However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.

%Authentication generally requires secrets.  Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
%
%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
%It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
%the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
%Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.  This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.  
%
%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high. However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.  
%
%The minimum necessary  entropy loss has been quantified in past work.  Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
%
%\paragraph {Our Contributions}
%To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
%The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.  
%
%On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful. We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
%%Furthermore, we have (asymptotic)~constructions that meet these bounds.
%
%On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction. The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.  This string $\recout$ is  required to have high HILL entropy even conditioned on $s$. Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
%
%Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
%~\ref{thm:lossless secure extractor log})).  We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult. 
%
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
%
%Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.  To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).  We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.  The LWE error vector, in our case, is the input $w$ itself.  To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution. We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed). This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).
\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. %We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $Z^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.

@@

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.  can we change this $d$ to $\mathsf{dis}$?}

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
U_d \times Y) \le \epsilon$.
\end{definition}

%In \secref{sec:impossCompSecSketch} we will use a slightly weaker notion, in which \rec is allowed to fail with small probability.\lnote{Can we add a comment that this corresponds to errors that can depend on the input but not the sketch? It's not obvious from the way this is written.} \lnote{can we just have a single definition --- the one below --- instead of two?}
%\begin{definition}
%We say that pair of procedures $(\sketch, \rec)$ is $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$ is an \emph{approximately correct secure sketch} if \defref{def:secure sketch} holds with correctness replaced with the following property, $\forall w, w'$ such that $\dis(w, w')\leq t$:
%\[
%\Pr[\rec(w', \sketch(w)) = w]\geq 1-\epsilon.
%\] where the probability is taken over the coins of \sketch and \rec.
%\end{definition}
\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.  Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).

>>>>

Authentication generally requires a secret drawn from some high-entropy source.  One of the primary building blocks for authentication is reliable key derivation.  Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).  The setting 
consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).  The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.  This information allows
the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.  This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.

Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and are defined (traditionally) as information-theoretic objects.  The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$. 
A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.

@@

The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.  Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.

@@

@@

@@

\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.  They can be constructed, for example, by applying a pseudorandom generator to the output of an information-theoretic extractor.  One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.   However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.  Furthermore, this approach does not allow the use of private randomness; private randomness is a crucial ingredient in our construction.
We compare the two approaches in \secref{sec:prg based comparison}.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $\mathcal{Z}$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $\mathcal{Z}^n$, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose t} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
Usually, we use bold letters for vectors or matrices, capitalized letters for random variables, and lowercase letters for elements in a vector or samples from a random variable.

@@

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
U_d \times Y) \le \epsilon$.
\end{definition}

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.  Also, for notational convenience, we modify the definition so that we can specify a general class of sources for which the fuzzy extractor is designed to work, rather than limiting ourselves to the class of sources that consists of all sources of a given min-entropy $m$, as in definitions above (of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.

\textbf{Remark}  Fuzzy extractor definitions make no guarantee about \rep behavior when the distance between $w$ and $w'$ is larger than $t$.  In the information-theoretic setting this seemed inherent as the ``correct'' $R$ should be information-theoretically unknown conditioned on $P$.  However, in the computationally setting this is not true.  Looking ahead, in our construction $R$ is information-theoretically determined conditioned on $P$~(with high probability over the coins of \gen).  Our $\rep$ algorithm will never output an incorrect key~(with high probability over the coins of \gen) but may not terminate.  However, it is not clear this is the desired behavior.  For this reason, we leave the behavior of \rep ambiguous when $\dis(w, w')>t$.

\section{Impossibility of Computational Secure Sketches}
\label{sec:impossCompSecSketch}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.  We consider two different notions for computational entropy, and for both of them show that corresponding secure sketches are subject to the same upper bounds as those for information-theoretic secure sketches. Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help.
